### 2019-03-23 reports/thesis/chapters/5_inference.tex
Put defectExample script together

\afterpage{\clearpage}
\subsection{Contaminated Experiment}

@@

\subsection{Contaminated Defect Experiment}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ dust defect Gaussian image with/without contamination and after filtering with kernel radius 20. Defected pixels have the distribution $\normal(3,1)$. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
  \label{fig:inference_saltDefect}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ line defect Gaussian image with/without contamination and after filtering with kernel radius 20. Defected pixels have the distribution $\normal(3,1)$. The line is 5 pixels thick. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
  \label{fig:inference_lineDefect}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 20. Defected pixels have the distribution $\normal(3,1)$. The square is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
  \label{fig:inference_squareDefect}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 40. Defected pixels have the distribution $\normal(3,1)$. The square is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
  \label{fig:inference_square2Defect}
\end{figure}

@@

\begin{figure}[htp]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_roc.eps}
        \caption{Dust defect $\pi_1=0.1$, $r=20$}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_roc.eps}
        \caption{5 pixels thick line defect, $r=20$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_roc.eps}
        \caption{$30\times 30$ square defect, $r=20$}
        \label{fig:inference_defectSimulationRoc_square20}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_roc.eps}
        \caption{$30\times 30$ square defect, $r=40$}
      \end{subfigure}
    }
  \caption{ROC curves for various defected $256\times 256$ Gaussian images. The difference curves show the results for the non-contaminated image, contaminated image, and filtered contaminated image. Defected pixels have the distribution $\normal(3,1)$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
  \label{fig:inference_defectSimulationRoc}
\end{figure}

>>>>

\afterpage{\clearpage}
\subsection{Detecting Defects Experiment}

@@

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ dust defect Gaussian image with/without contamination and after filtering with kernel radius 20. Defected pixels have the distribution $\normal(3,1)$. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
  \label{fig:inference_saltDefect}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ line defect Gaussian image with/without contamination and after filtering with kernel radius 20. Defected pixels have the distribution $\normal(3,1)$. The line is 5 pixels thick. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
  \label{fig:inference_lineDefect}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 20. Defected pixels have the distribution $\normal(3,1)$. The square is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
  \label{fig:inference_squareDefect}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 40. Defected pixels have the distribution $\normal(3,1)$. The square is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
  \label{fig:inference_square2Defect}
\end{figure}

@@

\begin{figure}[htp]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_roc.eps}
        \caption{Dust defect $\pi_1=0.1$, $r=20$}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_roc.eps}
        \caption{5 pixels thick line defect, $r=20$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_roc.eps}
        \caption{$30\times 30$ square defect, $r=20$}
        \label{fig:inference_defectSimulationRoc_square20}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_roc.eps}
        \caption{$30\times 30$ square defect, $r=40$}
      \end{subfigure}
    }
  \caption{ROC curves for various defected $256\times 256$ Gaussian images. The difference curves show the results for the non-contaminated image, contaminated image, and filtered contaminated image. Defected pixels have the distribution $\normal(3,1)$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
  \label{fig:inference_defectSimulationRoc}
\end{figure}
